\Huge Conferences in an Era of Expensive Carbon

### 2019-06-18 main.tex
Work.

How should ACM respond to these facts?  We have two concrete proposals.

@@

  \begin{itemize}
  \item Proposal: Every ACM-sponsored conference should be required to
  publicly report its carbon footprint (total and per-participant).
  (Including PC meetings, participant travel, maybe hotel?).
  \item ACM needs to provide tools to help conferences do this.  (SIGPLAN
  built one.)
  \item Benefits:
  \begin{itemize}
  \item Encourages people to pay attention, which will lead to some changes
  in behavior all by itself. 
  \item Generates data that will be needed for grounding discussions of how
  optimize footprint.  E.g., SIGPLAN has mostly gone to virtual PC
  meetings.  Livestreaming.
  \end{itemize}
\end{itemize}

These are things that we can and should be doing now.  Indeed, many parts
of ACM are already doing them.  (In SIGPLAN, we have... and the experience
has been...)

@@

But there is another, deep reason why going beyond simple measures is hard:
while conferences damage the climate, they also create significant value!
Science is a fundamentally social process, and the conference system
accelerates research through high-bandwidth interaction, direct
dissemination of results, network building, and serendipitous
cross-fertilization.

This presents a puzzle: How can we weigh the environmental harm caused by
conference travel against the social benefits of the scientific progress
that comes from conferences?  The question is difficult because the harm and
the compensating benefits cannot be directly compared---they are apples and
oranges.

  \begin{itemize}
  \item To motivate more painful changes and force people to make difficult
  choices, we need a price on carbon.
  \item Ultimately, governments should do this.  But we don't need to wait:
  as several companies have shown, even an artificial ``internal price'' on
  carbon creates a significant price signal that shapes behavior.
  \item Our second (more ambitious) proposal is: ACM should begin requiring
  conferences to pay a surcharge based on their carbon footprint.  It should
  be low at the beginning and increase steadily (and predictably) year on year.
  \item Benefit: This will create concrete downward pressure on conferences
  to decrease their footprints.  They can then choose (on the basis of
  careful analysis of data and weighing of benefits) how best to do so.
  \item The money raised in this way can be used in many ways: buying carbon
  offsets, supporting ``green computing research'', virtualizing conferences
  (livestreaming, etc.), supporting a transition to a low-carbon / few
  conferences business model for ACM.
  \end{itemize}

>>>>

How should ACM respond to these facts?  We have two concrete
proposals. First, all ACM conferences should publicly account for CO2e
spent as a result of hosting them. Second, ACM should embrace putting
a \emph{price} on carbon in conference budgets, to create pressure on
organizers to reduce its consumption.

@@

Our first proposal is simple: Every ACM-sponsored conference should
publicly report its carbon footprint, total and per-participant. A
conference's footprint will be dominated by participants' air travel,
but the accounting should not be limited to that: It should also
include air travel to in-person PC meetings, and estimate hotel and
food CO2e costs.

We hope that a public accounting will nudge conference organizers and
attendees to change their behavior. As an analogy: Chain restaurants
in the US are required by law to post calorie counts of food items on
menu boards, and studies show that enlightened customers order, on
average, up to 50 fewer calories a day, as a
result~\cite{menu}.

ACM can provide tools to help organizers account for this
footprint. We recently worked with the ACM SGB to develop an air
travel-focused CO2e calculator. One can input a CSV with registration
data, and the calculator will compute the estimated CO2e cost of air
travel for those sufficiently far away. This calculator could be
expanded to support related costs.

SIGPLAN has been thinking about how to reduce CO2e usage over the past
couple of years, informed by an accounting of CO2e expenditures. Doing
so has led several conference organizers \mwh{name which conferences}
to switch from holding in-person PC meetings to holding the meetings
on-line instead. \mwh{Mention Jens survey here.} It has also prompted
adding support for conference livestreaming (to go with talk
recording) to permit remote participation.

Most recently, we have been investigating how to purchase \emph{carbon
  offsets} to defray CO2e costs.
%
A carbon offset is sold by a vendor who uses the raised funds to
finance an activity that permanently avoids emitting an amount of
greenhouse gases. That the CO2e emission avoidance is truth and not
appearance can be certified by a watchdog organization. Typically,
planting trees is not a certifiable activity (since it's hard to
guarantee the trees won't be cut down), but installing methane capture
devices on landfill sites or buying fuel-efficient stoves to replace
open-fire cooking in poor communities can be.

Many organizations (including companies such as Google, Dell,
Microsoft, General Motors, Delta Airlines, Lyft, and Expedia, numerous
universities, and a number of academic societies) now buy carbon
offsets in order to reduce their overall footprint. ACM conferences
could do the same, and the purchases would be included in their public
accounting. We have been investigating this possibility for the past
year. ACM has now agreed that conference attendees can opt to purchase
an offset during registration, and ACM will use the designated funds
to purchase an offset. Even getting to this stage required some
investigation of the legality of ACM making the purchase on behalf of
the registrant~\cite{CarbonOFfsetReport}. Ideally, the purchase of
offsets would be made even simpler, but doing so requires further
thought.

Publicly accounting for CO2e expenditures will incentivize eliminating
CO2e-consuming activities whose corresponding value to the conference
is likely to be low. But a public accounting is unlikely to
incentivize major CO2e reductions, since these will require
significant changes to conference system itself, which may negatively
impact the value that conferences provide. 
%
Science is a fundamentally social process, and the conference system
accelerates research through high-bandwidth interaction, direct
dissemination of results, network building, and serendipitous
cross-fertilization.
%
Organizers and attendees will be reticent to harm the scientific
benefits they have all regularly experienced.

(Mike: I think we can significantly trim the text below. Instead, we can
talk here about a carbon tax as the next natural step. It can be
related to the sugar tax that some municipalities have imposed; when
public calorie counts are not enough to discourage use, add a tax
instead. The arc from the bullet list can come earlier, basically.)

Thus we have the question of apples and oranges: How can we weigh the
environmental harm caused by conference travel against the social
benefits of the scientific progress that comes from conferences?

% The question is difficult because the harm and
% the compensating benefits cannot be easily compared---they are apples and
% oranges.

  \begin{itemize}
  \item To motivate more painful changes and force people to make difficult
  choices, we need a price on carbon.
  \item Ultimately, governments should do this.  But we don't need to wait:
  as several companies have shown, even an artificial ``internal price'' on
  carbon creates a significant price signal that shapes behavior.
  \item Our second (more ambitious) proposal is: ACM should begin requiring
  conferences to pay a surcharge based on their carbon footprint.  It should
  be low at the beginning and increase steadily (and predictably) year on year.
  \item Benefit: This will create concrete downward pressure on conferences
  to decrease their footprints.  They can then choose (on the basis of
  careful analysis of data and weighing of benefits) how best to do so.
\item The money raised in this way can be used in many ways: buying
  carbon offsets (Mike: could include text from below on this),
  supporting ``green computing research'', virtualizing conferences
  (livestreaming, etc.), supporting a transition to a low-carbon / few
  conferences business model for ACM.
  \end{itemize}

(Mike: Need to include somewhere above:)

@@
